# /////////////////////////////////////////////////
# Sensitivity analysis disease,post process
# /////////////////////////////////////////////////

# This markdown file is used to create the visualisations and numeric analysis 
# presented as part of the sensitivity analysis of the disease parameters

# Setup
```{r}
library(tidyverse)
library(patchwork)
# Set working director
sep_setting <- function(df) {
  df %>% 
    mutate(sar = case_when(str_detect(setting, "hha_0.02094982") ~ 0.02,
                           str_detect(setting, "hha_0.2") ~ 0.2,
                           TRUE ~ 0.4),
           acf = case_when(str_detect(setting, "_acf_10") ~ 10,
                           str_detect(setting, "_acf_25") ~ 25,
                           str_detect(setting, "_acf_50") ~ 50,
                           str_detect(setting, "_acf_5") ~ 5,
                           TRUE ~ 0)
    )
}

sim_day_to_year_month <- function(df) {
  df <- df %>% 
    mutate(date = sim_start_date+day,
           year_month = as.Date(
             paste0(lubridate::year(date),"-",
                    lubridate::month(date),"-01"))
           ) %>% 
    select(-date) 
  return(df)
}
```

# HHS
## Get data
```{r}
test_dir_outputs <- file.path("intervention_hhs")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)


sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]
    csv_list[[j]] <- df
    index <- index + 1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_hhs <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
baseline_cum_inc <- data_hhs %>% 
  filter(str_detect(setting, "hhs_0")) %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% # We want 10 year cumulative incidence after run-in
  reframe(cum_inc = sum(inc), .by = c(setting, index)) # sum inc by parameter combination and run index

rm(data_hhs)
```

# Nu
## Get data
```{r}
test_dir_outputs <- file.path("SA_nu")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  
    
    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_nu <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
nu_inc <- data_nu %>% 
  select(day, inc, setting, index) %>% 
  reframe(inc = mean(inc), .by = c(day, setting)) %>% 
  sim_day_to_year_month() %>% 
  reframe(inc = sum(inc), .by = c(year_month, setting))

nu_cum_inc <- data_nu %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```

## Calc difference
```{r}
baseline_setting <- rep(unique(baseline_cum_inc$setting), each = 4)
intervention_setting <- unique(nu_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- nu_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
result <- result %>% 
  mutate(nu = rep(c(0.189, 0.1995,0.2205,0.231),3),
         hha = case_when(str_detect(setting, "hha_0.4") ~ 0.4,
                         str_detect(setting, "hha_0.2") ~ 0.2,
                         TRUE ~ 0.02))
p1 = result %>% 
  ggplot() +
  geom_point(aes(nu, mean)) +
  geom_errorbar(aes(nu, ymin = ci_lower, ymax = ci_upper), width = mean(result$nu)/40) +
  facet_wrap(~hha, nrow = 3) +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = expression(paste(nu)),
       y = "% change") +
  theme_bw() +
  theme(legend.position = "none")

rm(data_nu)
```

# Phi
## Get data
```{r}
test_dir_outputs <- file.path("SA_phi")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  
    
    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_phi <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
phi_inc <- data_phi %>% 
  select(day, inc, setting, index) %>% 
  reframe(inc = mean(inc), .by = c(day, setting)) %>% 
  sim_day_to_year_month() %>% 
  reframe(inc = sum(inc), .by = c(year_month, setting))

phi_cum_inc <- data_phi %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```

## Calc difference
```{r}
baseline_setting <- rep(unique(baseline_cum_inc$setting), each = 4)
intervention_setting <- unique(phi_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- phi_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
result <- result %>% 
  
  mutate(phi = rep(c(0.045, 0.0475,0.0525,0.055),3),
         hha = case_when(str_detect(setting, "hha_0.4") ~ 0.4,
                         str_detect(setting, "hha_0.2") ~ 0.2,
                         TRUE ~ 0.02))
p2 = result %>%   
  ggplot() +
  geom_point(aes(phi, mean)) +
  geom_errorbar(aes(phi, ymin = ci_lower, ymax = ci_upper), width = mean(result$phi)/40) +
  facet_wrap(~hha, nrow = 3) +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = "Prop fast progressors",
       y = "") +
  scale_x_continuous(breaks = seq(0.045,0.055, 0.0025)) +
  theme_bw() +
  theme(legend.position = "none")

rm(data_phi)
```


## Tabular presentation
### Sensitivity to phi
```{r}
result %>% 
  group_by(phi) %>% 
  summarise_all(mean) %>% 
  mutate(across(mean:ci_upper, ~round(.x,1)))
  
```



# Eta
## Get data
```{r}
test_dir_outputs <- file.path("SA_eta")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  
    
    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_eta <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
eta_inc <- data_eta %>% 
  select(day, inc, setting, index) %>% 
  reframe(inc = mean(inc), .by = c(day, setting)) %>% 
  sim_day_to_year_month() %>% 
  reframe(inc = sum(inc), .by = c(year_month, setting))

eta_cum_inc <- data_eta %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```

## Calc difference
```{r}
baseline_setting <- rep(unique(baseline_cum_inc$setting), each = 4)
intervention_setting <- unique(eta_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- eta_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
result <- result %>% 
  mutate(eta = rep(c(0.000005479452055*0.9, 0.000005479452055*0.95, 0.000005479452055*1.05,0.000005479452055*1.1),3),
         hha = case_when(str_detect(setting, "hha_0.4") ~ 0.4,
                         str_detect(setting, "hha_0.2") ~ 0.2,
                         TRUE ~ 0.02))
p3 = result %>%   
  ggplot() +
  geom_point(aes(eta, mean)) +
  geom_errorbar(aes(eta, ymin = ci_lower, ymax = ci_upper), width = mean((result$eta))/40) +
  facet_wrap(~hha, nrow = 3) +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = expression(paste(eta)),
       y = "") +
  scale_x_continuous(breaks = c(0.000005479452055*0.925, 0.000005479452055,0.000005479452055*1.075),
                       label = function(x) {
    parse(text=gsub("e", " %*% 10^", scales::scientific_format()(x)))}
  )+
  theme_bw() +
  theme(legend.position = "none")

rm(data_eta)
```


# Mu
## Get data
```{r}
test_dir_outputs <- file.path("SA_mu")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  
    
    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_mu <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
mu_inc <- data_mu %>% 
  select(day, inc, setting, index) %>% 
  reframe(inc = mean(inc), .by = c(day, setting)) %>% 
  sim_day_to_year_month() %>% 
  reframe(inc = sum(inc), .by = c(year_month, setting))

mu_cum_inc <- data_mu %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```

## Calc difference
```{r}
baseline_setting <- rep(unique(baseline_cum_inc$setting), each = 4)
intervention_setting <- unique(mu_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- mu_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
result <- result %>% 
  
  mutate(mu = rep(c(0.001065753*0.9,0.001065753*0.95, 0.001065753*1.05, 0.001065753*1.1),3),
         hha = case_when(str_detect(setting, "hha_0.4") ~ 0.4,
                         str_detect(setting, "hha_0.2") ~ 0.2,
                         TRUE ~ 0.02)) 
p4 = result %>% 
  ggplot() +
  geom_point(aes(mu, mean)) +
  geom_errorbar(aes(mu, ymin = ci_lower, ymax = ci_upper), width = mean(result$mu)/40) +
  facet_wrap(~hha, nrow = 3) +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = expression(paste(mu)),
       y = "% change") +
  scale_x_continuous(breaks = round(c(0.001065753*0.925,0.001065753, 0.001065753*1.075), 5)) +
  theme_bw() +
  theme(legend.position = "none")

rm(data_mu)
```

# Alpha
## Get data
```{r}
test_dir_outputs <- file.path("SA_alpha")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  
    
    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_alpha <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
alpha_inc <- data_alpha %>% 
  select(day, inc, setting, index) %>% 
  reframe(inc = mean(inc), .by = c(day, setting)) %>% 
  sim_day_to_year_month() %>% 
  reframe(inc = sum(inc), .by = c(year_month, setting))

alpha_cum_inc <- data_alpha %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```

## Calc difference
```{r}
baseline_setting <- rep(unique(baseline_cum_inc$setting), each = 4)
intervention_setting <- unique(alpha_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- alpha_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
result <- result %>% 
  
  mutate(alpha = rep(c(0.00006191781*0.9,0.00006191781*0.95, 0.00006191781*1.05, 0.00006191781*1.1),3),
         hha = case_when(str_detect(setting, "hha_0.4") ~ 0.4,
                         str_detect(setting, "hha_0.2") ~ 0.2,
                         TRUE ~ 0.02)) 

p5 = result %>% 
  ggplot() +
  geom_point(aes(alpha, mean)) +
  geom_errorbar(aes(alpha, ymin = ci_lower, ymax = ci_upper), width = mean(result$alpha)/40) +
  facet_wrap(~hha, nrow = 3) +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = expression(paste(alpha)),
       y = "") +
  scale_x_continuous(breaks = c(0.00006191781*0.925,0.00006191781, 0.00006191781*1.075),
                       label = function(x) {
    parse(text=gsub("e", " %*% 10^", scales::scientific_format()(x)))}
  ) +
  theme_bw() +
  theme(legend.position = "none")

rm(data_alpha)
```

# Tau
## Get data
```{r}
test_dir_outputs <- file.path("SA_tau")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  
    
    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_tau <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
tau_inc <- data_tau %>% 
  select(day, inc, setting, index) %>% 
  reframe(inc = mean(inc), .by = c(day, setting)) %>% 
  sim_day_to_year_month() %>% 
  reframe(inc = sum(inc), .by = c(year_month, setting))

tau_cum_inc <- data_tau %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```

## Calc difference
```{r}
baseline_setting <- rep(unique(baseline_cum_inc$setting), each = 4)
intervention_setting <- unique(tau_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- tau_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
result <- result %>% 
  
  mutate(tau = rep(c(573.05*0.9,573.05*0.95, 573.05*1.05, 573.05*1.1),3),
         hha = case_when(str_detect(setting, "hha_0.4") ~ 0.4,
                         str_detect(setting, "hha_0.2") ~ 0.2,
                         TRUE ~ 0.02)) 

p6 = result %>% 
  ggplot() +
  geom_point(aes(tau, mean)) +
  geom_errorbar(aes(tau, ymin = ci_lower, ymax = ci_upper), width = mean(result$tau)/40) +
  facet_wrap(~hha, nrow = 3) +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = expression(paste(tau)),
       y = "") +
  scale_x_continuous(breaks = c(525, 550, 575, 600, 625)) +
  theme_bw() +
  theme(legend.position = "none") 

rm(data_tau)
```


# Save plot
```{r}
(p1 | p2 | p3) / (p4 | p5 | p6)
ggsave("sa_disease.pdf", height = 8, width = 9)
rm(all_csv)
```


