# /////////////////////////////////////////////////
# Sensitivity analysis intervention,post process
# /////////////////////////////////////////////////

# This markdown file is used to create the visualisations and numeric analysis 
# presented as part of the sensitivity analysis of the intervention

# Setup
```{r}
library(tidyverse)
library(patchwork)
# Set working director
sep_setting <- function(df) {
  df %>% 
    mutate(sar = case_when(str_detect(setting, "hha_0.02094982") ~ 0.02,
                           str_detect(setting, "hha_0.2") ~ 0.2,
                           TRUE ~ 0.4),
           acf = case_when(str_detect(setting, "_acf_10") ~ 10,
                           str_detect(setting, "_acf_25") ~ 25,
                           str_detect(setting, "_acf_50") ~ 50,
                           str_detect(setting, "_acf_5") ~ 5,
                           TRUE ~ 0)
    )
}

sim_day_to_year_month <- function(df) {
  df <- df %>% 
    mutate(date = sim_start_date+day,
           year_month = as.Date(
             paste0(lubridate::year(date),"-",
                    lubridate::month(date),"-01"))
           ) %>% 
    select(-date) 
  return(df)
}
```

# Baseline data
## HHS only
```{r}
test_dir_outputs <- file.path("intervention_hhs")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)


sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]
    csv_list[[j]] <- df
    index <- index + 1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_hhs <- do.call(rbind, all_csv)

hhs_cum_inc <- data_hhs %>% 
  filter(str_detect(setting, "hhs_1")) %>% 
  filter(day>9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index)) %>% 
  sep_setting()

baseline_cum_inc <- data_hhs %>% 
  filter(str_detect(setting, "hhs_0")) %>% 
  filter(day>9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index)) %>% 
  sep_setting()

rm(data_hhs)
```

## ACF
```{r}
test_dir_outputs <- file.path("intervention_acf")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]
    csv_list[[j]] <- df
    index <- index + 1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_acf <- do.call(rbind, all_csv)

acf_cum_inc <- data_acf %>% 
  filter(str_detect(setting, "hhs_1")) %>% 
  filter(day>9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index)) %>% 
  sep_setting()

rm(data_acf)
```


# Sensitivity
## Get data
```{r}
test_dir_outputs <- file.path("SA_sensitivity")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  

    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_sens <- do.call(rbind, all_csv)
```

## Calc inc
```{r}
sens_inc <- data_sens %>% 
  select(day, inc, setting, index) %>% 
  reframe(inc = mean(inc), .by = c(day, setting)) %>% 
  sim_day_to_year_month() %>% 
  reframe(inc = sum(inc), .by = c(year_month, setting))

sens_cum_inc <- data_sens %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))

sens_baseline_cum_inc <- hhs_cum_inc %>% 
  filter(!str_detect(setting, "hha_0.2")) %>% 
  rbind(
    acf_cum_inc %>% 
      filter(!str_detect(setting, "hha_0.2")) %>% 
      filter(str_detect(setting, "acf_50"))
  )
```

## Calc difference
```{r}
baseline_setting <- rep(unique(sens_baseline_cum_inc$setting), each = 7)
baseline_setting <- baseline_setting[order(baseline_setting)]

intervention_setting <- unique(sens_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- sens_baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- sens_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
p1 = result %>% 
  mutate_if(is.numeric, round) %>% 
  mutate(sens = as.numeric(str_sub(setting, -3,-1)),
         acf = ifelse(str_detect(setting, "acf_50"), 50, 0),
         sar = ifelse(str_detect(setting, "hha_0.4"), 0.4, 0.02)) %>% 
  mutate(sens = ifelse(acf == 0, sens-0.01, sens+0.01)) %>%  # jitter
  ggplot() +
  geom_point(aes(sens, mean, colour = as.factor(acf))) +
  geom_errorbar(aes(sens, ymin = ci_lower, ymax = ci_upper, color = as.factor(acf)), width = 0.02) +
  facet_wrap(~sar, nrow = 2) +
  scale_color_manual(values = c("#00468BFF", "#ED0000FF"), name = "ACF") +
  scale_x_continuous(breaks = seq(0.3, 0.9, 0.1)) +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = "Test sensitivity",
       y = "% change") +
  theme_bw() +
  theme(legend.position = "none")
```

## Tabular presentation
### Absolute impact of sensitivity = 0.3
```{r}
intervention_setting <- unique(sens_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- baseline_cum_inc %>% 
    pull(cum_inc)
  
  intervention <- sens_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])
  result$ci_lower[i] <- test$conf.int[1]
  result$ci_upper[i] <- test$conf.int[2]
}

result %>% 
  mutate(hha = c(rep(0.02, 14), rep(0.4, 14)),
         acf = rep(c(rep(0, 7), rep(50, 7)), 2),
         sens = rep(seq(0.3, 0.9, 0.1), 4)
         ) %>% 
  filter(sens == 0.3) %>% 
  mutate_if(is.numeric, round)
```

# Delta
## Get data
```{r}
test_dir_outputs <- file.path("SA_delta")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  

    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_delta <- do.call(rbind, all_csv)
```


## Calc inc
```{r}
delta_cum_inc <- data_delta %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```


## Calc difference
```{r}
baseline_setting <- rep(unique(sens_baseline_cum_inc$setting), each = 4)
baseline_setting <- baseline_setting[order(baseline_setting)]

intervention_setting <- unique(delta_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- sens_baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- delta_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
p2 = result %>% 
  mutate_if(is.numeric, round) %>% 
  sep_setting() %>% 
  mutate(delta = rep(c(0.009, 0.0095, 0.0105,0.011),4)) %>% 
  filter(delta != 0.1) %>% 
  mutate(delta = ifelse(acf == 0, delta+0.00006, delta-0.00006)) %>% # jitter
  ggplot() +
  geom_point(aes(delta, mean, colour = as.factor(acf))) +
  geom_errorbar(aes(delta, ymin = ci_lower, ymax = ci_upper, color = as.factor(acf)), width = 0.0001) +
  facet_wrap(~sar,nrow=2) +
  scale_color_manual(values = c("#00468BFF", "#ED0000FF"), name = "ACF") +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = expression(paste(delta[2])),
       y = "") +
  theme_bw() +
  theme(legend.position = "top")

rm(data_delta)
```


## Taublar presentation
### sensitivity delta
```{r}
result %>% 
  mutate(hha = c(rep(0.02, 8), rep(0.4, 8)),
         acf = rep(c(rep(0, 4), rep(50, 4)), 2),
         delta = rep(c(0.009, 0.0095, 0.0105, 0.011), 4)
         ) %>% 
  mutate(across(mean:ci_upper, ~ round(.x,1))) %>% 
  filter(delta == 0.009 | delta == 0.011) %>% 
  arrange(desc(mean))
```

# Phase
## Get data
```{r}
test_dir_outputs <- file.path("SA_phase")
all_configs_dirs <- list.dirs(test_dir_outputs, recursive = FALSE)

sim_start_date <- as.Date("2031-01-01")-12652

pattern_name <- "_sim_table.csv"
all_csv <- list()
index <- 1
for (i in seq_along(all_configs_dirs)) {
  csv_list <- list()
  csv_files <- list.files(path = file.path(all_configs_dirs[i], "outputs"),
                          pattern = pattern_name, full.names = TRUE)
  for (j in seq_along(csv_files)) {
    df <- data.table::fread(csv_files[j])
    df[, setting := sub("^[^/]*/", "", all_configs_dirs[i])]
    df[, index := index]  

    csv_list[[j]] <- df
    index <- index +1
  }
  all_csv[[i]] <- do.call(rbind, csv_list) 
}

data_phase <- do.call(rbind, all_csv)
```


## Calc inc
```{r}
phase_cum_inc <- data_phase %>% 
  select(day, inc, index, setting) %>% 
  filter(day >= 9000) %>% 
  reframe(cum_inc = sum(inc), .by = c(setting, index))
```


## Calc difference
```{r}
baseline_setting <- rep(unique(sens_baseline_cum_inc$setting), each = 5)
baseline_setting <- baseline_setting[order(baseline_setting)]

intervention_setting <- unique(phase_cum_inc$setting)

result <- tibble(setting = seq_along(intervention_setting),
                 mean = c(1),
                 ci_lower = c(1),
                 ci_upper = c(1))

for(i in seq_along(intervention_setting)) {
  control <- sens_baseline_cum_inc %>% 
    filter(setting == baseline_setting[i]) %>% 
    pull(cum_inc)
  
  intervention <- phase_cum_inc %>% 
    filter(setting == intervention_setting[i]) %>% 
    pull(cum_inc)
  
  test <- t.test(intervention, control)
  
  result$setting[i] <- intervention_setting[i]
  result$mean[i] <- as.numeric(test$estimate[1]-test$estimate[2])/test$estimate[2]*100
  result$ci_lower[i] <- test$conf.int[1]/test$estimate[2]*100
  result$ci_upper[i] <- test$conf.int[2]/test$estimate[2]*100
}
```

## Visualise difference
```{r}
p3 = result %>% 
  mutate_if(is.numeric, round) %>% 
  sep_setting() %>% 
  mutate(phase = rep(c(1080, 360, 540,720, 900),4)) %>% 
  mutate(phase = ifelse(acf == 0, phase-15, phase+15)) %>% # jitter
  ggplot() +
  geom_point(aes(phase, mean, colour = as.factor(acf))) +
  geom_errorbar(aes(phase, ymin = ci_lower, ymax = ci_upper, color = as.factor(acf)), width = 30) +
  facet_wrap(~sar, nrow = 2) +
  scale_color_manual(values = c("#00468BFF", "#ED0000FF"), name = "ACF") +
  geom_hline(aes(yintercept = 0), lty = "dashed") +
  labs(x = "Intervention phase-in",
       y = "") +
  theme_bw() +
  theme(legend.position = "none") 

rm(data_phase)
```

# Save plot
```{r}
p1 | p2 | p3

ggsave("sa_intervention.pdf", height = 5, width = 8)
```

```{r}
rm(all_csv)
```
